\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2020-05-02 ase20/conclusion.tex
[ASE] Removed bigint-3 / Updated Table 5

\section{Conclusion}\label{sec:conclude}
Annual updates of ECMAScript make it difficult to build program
analysis or formal verification of JavaScript due to the required human efforts
in modeling a moving target.  In this paper, we proposed \( \tool \), a tool
that \textit{automatically} extracts the syntax and semantics as a parser and
an AST-IR translator from ECMAScript written in English.
The tool automatically extracts all the syntax and \inred{XX.XX\%} of the
semantics for the most recent four versions of ECMAScript (ES7 to ES10).
We evaluated the correctness of the tool by testing the extracted
semantics from ES10 with Test262, the official conformance suite.
Using \inred{X,XXX} failed tests, we found nine specification errors,
four of which are newly discovered, confirmed by TC39, and planned to
be integrated in ES11.  After fixing the errors, the extracted
semantics passed all \inred{XX,XXX} applicable tests in Test262.
We also showed that \( \tool \) is forward compatible by applying it to nine
proposals to be included in ES11, which let us find four errors in the
BigInt proposal.  We believe that \( \tool \) can dramatically reduce
human efforts in building various JavaScript tools correctly.

>>>>

\section{Conclusion}\label{sec:conclude}
Annual updates of ECMAScript make it difficult to build program
analysis or formal verification of JavaScript due to the required human efforts
in modeling a moving target.  In this paper, we proposed \( \tool \), a tool
that \textit{automatically} extracts the syntax and semantics as a parser and
an AST-IR translator from ECMAScript written in English.
The tool automatically extracts all the syntax and \inred{XX.XX\%} of the
semantics for the most recent four versions of ECMAScript (ES7 to ES10).
We evaluated the correctness of the tool by testing the extracted
semantics from ES10 with Test262, the official conformance suite.
Using \inred{X,XXX} failed tests, we found nine specification errors,
four of which are newly discovered, confirmed by TC39, and planned to
be integrated in ES11.  After fixing the errors, the extracted
semantics passed all \inred{XX,XXX} applicable tests in Test262.
We also showed that \( \tool \) is forward compatible by applying it to nine
proposals to be included in ES11, which let us find three errors in the
BigInt proposal.  We believe that \( \tool \) can dramatically reduce
human efforts in building various JavaScript tools correctly.

### 2020-05-02 ase20/eval.tex
[ASE] Removed bigint-3 / Updated Table 5

\begin{figure}[t]
  \centering
  \begin{subfigure}{0.48\textwidth}
    \includegraphics[width=\textwidth]{img/sem-all.pdf}
    \caption{For each ECMAScript version from ES7 to ES10}
    \label{fig:semantics-all-version}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.48\textwidth}
    \includegraphics[width=\textwidth]{img/sem-update.pdf}
    \caption{For each update between adjacent versions}
    \label{fig:semantics-all-version-update}
  \end{subfigure}
\vspace*{-.5em}
\caption{Semantics coverage: Number of algorithm steps in specifications,
from which \( \tool \) generated the semantics}
  \label{fig:all-version}
\vspace*{-1.5em}
\end{figure}

@@

    BigInt-3 &
    Number &
    \makecell[l]{Using {\bf ToUint32} instead of {\bf ToInt32} in {\bf
    NumberBitwiseOp}} &
    \textsf{X} &
    2019-09-27 &
    2020-04-23 &
    209 days &
    \inred{XX} \\\hline

    BigInt-4 &
    Number &
    \makecell[l]{Unhandling BigInt values in the {\bf Number} constructor} &
    \textsf{O} &
    2019-09-27 &
    2019-11-19 &
    53 days &
    \inred{XX}
  \end{tabular}
\end{table*}

@@

    \code{import()} &
    0 &
    2 &
    22/23 &
    0/0 &
    18,064/18,064\\\hline

    \code{BigInt} &
    4 &
    0 &
    258/323 &
    \inred{207}/207 &
    \inred{18,064}/18,064\\\hline

@@

    Optional Chaining &
    3 &
    3 &
    72/74 &
    19/19 &
    18,064/18,064\\\hline

@@

    {\bf Total} &
    8 &
    11 &
    502/577 &
  \end{tabular}
\vspace*{-1em}
\end{table}

@@

We applied \( \tool \) to all nine Finished proposals as shown in
Table~\ref{table:spec-prop-result}.
Collectively, the proposals modified eight lexical and
11 syntactic productions, and \( \tool \) successfully
synthesized parsers for them.  The synthesized parsers parse all
applicable tests for all proposals.  For abstract algorithms,
\inred{XXX} steps out of \inred{XXX} are automatically converted to
corresponding \( \ires \) instructions by \textsf{Algorithm Compiler}
without changing {\sf Compile Rules}.  Thus, \( \tool \) has the
success rate of \inred{XX.XX\%} on average for forthcoming proposals.

@@

Using the failed tests, we discovered four errors in the
BigInt proposal: three new errors (BigInt-1 to BigInt-3) and one known
error (BigInt-4) as summarized in Table~\ref{table:spec-errors}.
All of them were confirmed by TC39 and will be fixed in ES11.
The proposal added two new types: BigInt as a new type of primitives
and Numeric as a unified type of the original Number type and the new BigInt type.
Therefore, it not only added new algorithms for BigInt but also modified
all existing algorithms for Number values.
The error BigInt-1 is due to a misuse of the variable 
\code{oldValue} in {\bf Evaluation} of {\it UpdateExpression}.
BigInt-2 and BigInt-3 break the backward compatibility because of
misusing {\bf ToInt32} and {\bf ToUint32}
in unsigned right shift operators and bitwise operators, respectively.
BigInt-4 is due to missing BigInt primitives in the Number constructor.
On average, four errors existed for 170 days in the proposal.

>>>>

\begin{figure}[t]
  \centering
  \begin{subfigure}{0.48\textwidth}
    \includegraphics[width=\textwidth]{img/sem-all.pdf}
    \caption{For each ECMAScript version from ES7 to ES10}
    \vspace*{1.5em}
    \label{fig:semantics-all-version}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.48\textwidth}
    \includegraphics[width=\textwidth]{img/sem-update.pdf}
    \caption{For each update between adjacent versions}
    \label{fig:semantics-all-version-update}
  \end{subfigure}
\vspace*{-.5em}
\caption{Semantics coverage: Number of algorithm steps in specifications,
from which \( \tool \) generated the semantics}
  \label{fig:all-version}
\vspace*{-0.5em}
\end{figure}

@@

    BigInt-3 &
    Number &
    \makecell[l]{Unhandling BigInt values in the {\bf Number} constructor} &
    \textsf{O} &
    2019-09-27 &
    2019-11-19 &
    53 days &
    \inred{XX}
  \end{tabular}
\end{table*}

@@

    \code{import()} &
    0 &
    2 &
    38/38 &
    0/0 &
    18,064/18,064\\\hline

    \code{BigInt} &
    4 &
    0 &
    298/326 &
    \inred{207}/207 &
    \inred{18,064}/18,064\\\hline

@@

    Optional Chaining &
    3 &
    3 &
    74/74 &
    19/19 &
    18,064/18,064\\\hline

@@

    {\bf Total} &
    8 &
    11 &
    560/595 &
  \end{tabular}
\vspace*{-1em}
\end{table}

@@

We applied \( \tool \) to all nine Finished proposals as shown in
Table~\ref{table:spec-prop-result}.
Collectively, the proposals modified eight lexical and
11 syntactic productions, and \( \tool \) successfully
synthesized parsers for them.  The synthesized parsers parse all
applicable tests for all proposals.  For abstract algorithms,
560 steps out of 595 are automatically converted to
corresponding \( \ires \) instructions by \textsf{Algorithm Compiler}
without changing {\sf Compile Rules}.  Thus, \( \tool \) has the
success rate of 94.12\% on average for forthcoming proposals.

@@

Using the failed tests, we discovered three errors in the
BigInt proposal: two new errors (BigInt-1 and BigInt-2) and one known
error (BigInt-3) as summarized in Table~\ref{table:spec-errors}.
All of them were confirmed by TC39 and will be fixed in ES11.
The proposal added two new types: BigInt as a new type of primitives
and Numeric as a unified type of the original Number type and the new BigInt type.
Therefore, it not only added new algorithms for BigInt but also modified
all existing algorithms for Number values.
The error BigInt-1 is due to a misuse of the variable
\code{oldValue} in {\bf Evaluation} of {\it UpdateExpression}.
BigInt-2 breaks the backward compatibility because of
misusing {\bf ToInt32} instead of {\bf ToUint32}
in unsigned right shift operators.
BigInt-3 is due to missing BigInt primitives in the Number constructor.
On average, three errors existed for 157 days in the proposal.
